---
title: "9041 Lab 2"
author: Amitha Vallapuram
date: Oct 1 2026
format: 
    html:
      toc: true
      code-fold: true
      code-summary: "Show code"
      df-print: paged
execute:
    echo: false
    warning: false
---

Loading libraries

```{r, load libraries}
#| output: FALSE
# Output false ensures your reproducible document does not show all of your code!

# Remember to install packages you do not already have

library(tidyverse)
library(readxl)
library(psych)
library(gt)
library(janitor)
```

```{r}
#| output: FALSE

# Load data
data<-read_excel("./Attachment_Anxiety_Data.xlsx")


# Inspect data for the big five dataset
head(data)
```

```{r, clean data}
#| output: FALSE

# Use mutate to rename variables in a meaningful way - I did Gender and Ethnicity. 
# Mutate to convert survey response values to integers - I converted all numerical variables to integer format (this includes the demographic numerical variables)

AA.data.clean <- data |>
    mutate(Gender = case_when(Gender==1 ~ "Male", Gender==2 ~"Female", TRUE ~ "NA")) |> 
    mutate(Ethnicity = case_when(Ethnicity==1 ~ "white/Caucasian", Ethnicity==2 ~ "Asian/Asian British",Ethnicity==5 ~ "Other ethnic group", Ethnicity==6 ~ "prefer not to say", TRUE ~ "NA")) |> 
    select(URN:SEst_10) |>
    mutate(across(SA_1:SEst_10, as.integer))
```

```{r, score items}
#| output: FALSE

# Answer key: which items belong to each subscale.
# "-" marks reverse-coded items, which get flipped so higher scores always mean more of the trait.

keys <- list(SocialInteractionAnxiety=c("SA_1", "SA_2", "SA_3", "SA_4", "-SA_5", "SA_6", "SA_7", "SA_8", "-SA_9", "SA_10", "-SA_11", "SA_12", "SA_13", "SA_14", "SA_15", "SA_16", "SA_17", "SA_18", "SA_19", "SA_20"),
                AttachmentAnxiety=c("AA_1", "AA_2", "AA_3", "AA_4", "AA_5", "AA_6", "AA_7", "AA_8", "AA_9"),
                RosenbergSelfEsteem=c("SEst_1", "-SEst_2", "SEst_3", "SEst_4", "-SEst_5", "-SEst_6", "SEst_7", "-SEst_8", "-SEst_9", "SEst_10"))


# Average items per person, and compute Cronbach's alpha.
# The Lab instructions say social interaction anxiety go from 0 to 4 but I see in the excel sheet that they are going from
# 1-5 so I have set that as the min and max values.
scores_SA<-scoreItems(keys["SocialInteractionAnxiety"], AA.data.clean, totals = F, min=1, max=5)
scores_AA<-scoreItems(keys["AttachmentAnxiety"], AA.data.clean, totals = F, min=1, max=7)
scores_SEst<-scoreItems(keys["RosenbergSelfEsteem"], AA.data.clean, totals = F, min=1, max=4)

# Turn this into a dataframe!
scores_SA.df<-as.data.frame(scores_SA$scores)
scores_AA.df<-as.data.frame(scores_AA$scores)
scores_SEst.df<-as.data.frame(scores_SEst$scores)

allscores.df <- cbind(scores_SA.df, scores_AA.df, scores_SEst.df)
```

```{r, combine data frames}
#| output: FALSE

# Combine the original data set with the new scores dataframe
AA.data.clean<-cbind(AA.data.clean, allscores.df)

# Inspect new data set
head(AA.data.clean)
```

```{r, reduced data}
#| output: FALSE

# Select only for the columns which you want to appear in your final data table
AA.final<- AA.data.clean |>
    select("URN", "Consent", "Gender", "Age group", "Ethnicity", "SocialInteractionAnxiety", "AttachmentAnxiety", "RosenbergSelfEsteem") |>
    mutate_if(is.numeric, round, 2)

AA.final
```

```{r, reproducible table}

# Create a demographics table of education by gender
demographictable <- AA.final |>
  tabyl(Gender, Ethnicity)

# Create your reproducible gt table
gttable.1 <- demographictable |>
  gt() |>
  tab_header(
    title = md("*Distribution of Males and Females by Ethnicity*")
  )

```

```{r, reproducible table for big five scores}
#| output: FALSE

# Summary statistics for certain columns
summary <- describe(select(AA.final, SocialInteractionAnxiety:RosenbergSelfEsteem))
summary

# Label sample size for later in your reproducible document using describe
n <- (describe(AA.final))[1,2]

# Name an object of Scales so this can appear in your table
Scales <- c("SocialInteractionAnxiety", "AttachmentAnxiety",  "RosenbergSelfEsteem")

# Create a column called Subscales in your summary table
summary$Scales<- Scales

#Combine the three Cronbach's alpha values 
alphas <- round(c(
  scores_SA$alpha,
  scores_AA$alpha,
  scores_SEst$alpha
), 2)

# Select for only the columns which you want to appear in your final table
summary <- summary |>
    select(Scales, mean, median, sd, range) |>
       mutate_if(is.numeric, round, 2)

# Combine summary information with alpha values
final.reptable <- cbind(summary, alphas)

# Create a reproducible table
gttable.2<- gt(final.reptable) |>
    tab_header(
        title = md("*Descriptive Statistics for the Attachment and Social Anxiety Scales*")) |>
    tab_stubhead(label= "Composites")|>
    tab_spanner(
        label="Central Tendency",
        columns = c(mean, median)
    )|>
        tab_spanner(
        label="Variability",
        columns = c(sd, range)
        )|>
            tab_spanner(
        label="Reliability Values (Chronbach's alpha)",
        columns = alphas
            ) 

```

```{r, filtered dataset}
#| output: FALSE

# Use filter

AA.filtered <- AA.final |>
    filter(`Age group` == "1" | `Age group` == "2")

# Checking that age restriction worked
table(AA.filtered$`Age group`)
```
```{r, filtered score table}
#| output: FALSE

summary.filtered <- describe(select(AA.filtered, SocialInteractionAnxiety:RosenbergSelfEsteem))
n.filtered <- nrow(AA.filtered)
summary.filtered$Scales <- Scales

summary.filtered <- summary.filtered |>
    select(Scales, mean, median, sd, range) |>
    mutate_if(is.numeric, round, 2)

filtered.reptable <- cbind(summary.filtered, alphas)

# Create a reproducible table
gttable.3<- gt(filtered.reptable) |>
    tab_header(
        title = md("*Descriptive Statistics for the Attachment and Social Anxiety Scales (Age groups 1 and 2)*")) |>
    tab_stubhead(label= "Composites")|>
    tab_spanner(
        label="Central Tendency",
        columns = c(mean, median)
    )|>
        tab_spanner(
        label="Variability",
        columns = c(sd, range)
        )|>
            tab_spanner(
        label="Reliability Values (Chronbach's alpha)",
        columns = alphas
            ) 

```
## Intro

In this data set there were `{r} n` participants, with varying distributions of education type (Table 1).

`{r} gttable.1`

## Methods

### Participants


### Measures

The Attachment and Social Anxiety data set consists of 3 scales. The first one is the Social Interaction Anxiety Scale (Cronbach's alpha = `{r} alphas[1]`). The second one is the Experiences in Close Relationships Anxiety Subscale (Cronbach's alpha = `{r} alphas[2]`). The third one is the Rosenberg Self-Esteem Scale (Cronbach's alpha = `{r} alphas[3]`).


### Data Analysis Strategy
Here it is important to note that we have reverse keyed items 5, 9, and 11 in the Social
Interaction Anxiety Scale responses, and reverse keyed items 2, 5, 6, 8, and 9 in the Rosenberg
Self-Esteem Scale.

## Results
`{r} gttable.2`
In this data set, the 3 factors refer to the 3 composites that measure attachment and social anxiety. Participants had a mean score on social interaction anxiety of `{r} final.reptable[1,2]`, on experiences in close relationships anxiety of `{r} final.reptable[2,2]`, and on self-esteem of `{r} final.reptable[3,2]`.


`{r} gttable.3`
Here, we look at the attachment and social anxiety of participants over age 18 and below age 34.Participants had a mean score on social interaction anxiety of `{r} filtered.reptable[1,2]`, on experiences in close relationships anxiety of `{r} filtered.reptable[2,2]`, and on self-esteem of `{r} filtered.reptable[3,2]`.

## Discussion
